---
title: 'Homework #6'
author: "Elaine OldBear"
date: "4/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 25** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure need to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlap!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 
```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readxl)
library(ggrepel)
library(tidyr)

```

```{r}

kib <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet='Best in show full sheet')
head(kib)

tdog <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet='Best in show full sheet')
str(tdog)
tdog <- tdog %>% select(1, 3, 5, 6, 12, 32)
tdog <- tdog[-c(1:3), ]
head(tdog)
colnames(tdog) <- c("Breed", "Type", "Score", "Popularity", "Intelligence", "Size")
tdog <- tdog %>% mutate(
  Type = as.factor(Type),
  Score = as.numeric(Score),
  Popularity = as.numeric(Popularity),
  Intelligence = as.numeric(Intelligence)
)
tdog$Size <- factor(tdog$Size, levels=rev(levels(tdog$Size)))
levels(tdog$Type)
levels(tdog$Size)
?na.omit
#tdog <- na.omit(tdog)
```

```{r}
ggplot(tdog, aes(x=Score, y=Popularity, label=Breed)) +
  geom_point(aes(color=Type)) +
  labs(title = "Best in Show: THe Ultimate Data Dog", x="our data score", y="popularity") +
  geom_text_repel(aes(label=Breed), color="black", size=3)


```